% Copyright (c) Geoffrey Lentner 2015. All Rights Reserved.
% Academic/Source/Computation.tex


\section*{Software \& Programming}

\Descriptions
{
	\item[Unix >>] I have several years of experience developing in the unix environoment,
	including scripting and build tools (e.g., \textit{bash}, \textit{make}). I am also
	proficient using version control tools (e.g., \textit{git}) for collaborating with
	peers on software projects including the creation and merging of branches. My
	understanding of unix and all of the below listed tools and languages is entirely
	self taught. I am passionate about programming and building software tools for
	doing awesome things.

	\item[C++ >>] I enjoy the power and flexibility of C++ programming. I've developed a
	number of \href{http://github.com/glentner/Gaia-1.0}{\textbf{simulation codes}} and
	frameworks in C++. I am currently also collaborating with others to put together a
	new template library using the variability of C++14 for n-dimensional data structures
	for both tensor analysis and elemental operations. I am knowledgable in object oriented
	design, encapsulation, enheritance, RAII, multithreading, algorithms and data structures.

	\item[Python >>] I do a lot of work in Python (and consider myself an advocate for
	the adoption of Python 3 for scientific applications). Python's standard libraries
	and dynamically typed syntax make it very efficient for developing scientific
	applications. While I enjoy C++, Python is often the better tool for the job.

	\item[HTML >>] I have a working knowledge of HTML5, CSS3, Javascript, and PHP. I
	have maintained my own \href{http://glentner.github.io}{\textbf{website}} for years and
	have started to explore dynamic behavior and responsive design. I'm actually even
	working on a new (very lightweight) framework in Python to build and maintain HTML
	websites in a more object oriented fashion.

	\item[Open Source >>] I consider myself to be a proponent of open source. I enjoy
	contributing to open source projects. My \href{http://github.com/glentner}{\textbf{GitHub}}
	profile has quite a number of repositories of both
	\href{http://github.com/glentner/slipy}{\textbf{original work}} and forks of current projects.

	\item[Other Software >>] In addition to the above mentioned items I am proficient in
	a number of other software programs and languages, including MATLAB/Octave,
	Mathematic, ROOT, IRAF, DS9, and \LaTeX (to name a few).
}

\bigskip
