% Copyright (c) Geoffrey Lentner 2015. All Rights Reserved.
% Academic/Source/Research.html


\section*{Research Experience}



% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% MASTERS THESIS RESEARCH
\Experience
{
	\textbf{Master's Thesis}\\
	\href{http://www.physics.louisville.edu/jtl/}{James Lauroesch}
	(Advisor, Associate Professor)\\
	Department of Physics and Astronomy
}
{
	2014 - 2015\\
	University of Louisville
}
{
	\item Spectral analysis of stellar targets to identify ISM absorption from local cold
	cloud, with implications for our understanding of the Local Hot Bubble.

	\item Develop entire software framework (\href{http://github.com/glentner/slipy}{SLiPy})
	for automated calibration of absorption spectral data (e.g., telluric corrections,
	velocity calibrations) and interactive fitting of line profiles.

	\item Advanced scripting.
}





% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% PRIME Lab

\Experience
{
	\textbf{Undergraduate Controller}\\
	\href{http://www.physics.purdue.edu/people/faculty/mcaffee.html}{Marc Caffee}
	(Director of PRIME Lab, Professor)\\
	Department of Physics and Astronomy
}
{
	2012 - 2013\\
	Purdue University\\
	PRIME Lab
}
{
	\item A dedicated research and user facility for accelerator
	mass spectrometry with a 10 MeV Van de Graaff, tandem accelerator.

	\item Monitor data acquisition and control systems and record data; make adjustments
	and intervene at run time.

	\item Prepare new samples in clean room environment; install cathode wheels at the
	accelerator.
}




% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% XENON100 w/ Rafael

\Experience
{
	\textbf{Undergraduate Research Assistant}\\
	\href{http://www.physics.purdue.edu/people/faculty/lang.html}{Rafael Lang}
	(Assistant Professor)\\
	Department of Physics and Astronomy
}
{
	2011 - 2012\\
	Purdue University
}
{
	\item Research and development in collaboration with the Xenon100 experiment
	to directly detect dark matter (liquid nobel gas targets for detecting rare dark
	matter interactions via nuclear recoils).

	\item Design and construct photo-opaque test chamber to calibrate PMTs for single
	photon detection.
}





% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =
% Astro w/ Jaehyon

\Experience
{
	\textbf{Undergraduate Research Assistant}\\
	\href{http://www.physics.oregonstate.edu/~rheeja/}{Jaehyon Rhee}
	(Research Assistant Professor)\\
	Department of Physics and Astronomy
}
{
	2011\\
	Purdue University
}
{
	\item Image processing, photometry.
	\item Data reduction and elemental abundance analysis of very-metal-poor stars.
}
